### 2021-06-19 docs/manuscript/manuscript.tex
Add example of two-input network
Add range for diffusion parameters

However, although several studies have analyzed the properties of GRNs that
process positional information, they have focused on particular natural
networks~\cite{Schaerli2014,Jaeger2004}, in synthetic networks~\cite{Basu2005,
Reinitz1995,Schaerli2018,Elowitz2000}, or have constrained the
design of the GRNs to accept an input signal from only one of its nodes, which is
not always biologically realistic as multiple input systems can exist~\cite{Cotterell2010,
munteanu_2014, Schaerli2014}.

@@

% For figure citations, please use "Fig" instead of "Figure".
In order to study three-node GRNs we represented them by three sets of real
numbers, the first set was composed of the interaction values
between genes in the network; the second of the diffusion rates (D) of each of
the three gene products; and the third of the degradation rates ($\delta$) of
these same gene products, with $D$ and $\delta  \in [0, 0.05]$.\\

>>>>

However, although several studies have analyzed the properties of GRNs that
process positional information, they have focused on particular natural
networks~\cite{Schaerli2014,Jaeger2004}, in synthetic networks~\cite{Basu2005,
Reinitz1995,Schaerli2018,Elowitz2000}, or have constrained the
design of the GRNs to accept an input signal from only one of its nodes, which is
not always biologically realistic as multiple input systems can exist~\cite{Cotterell2010,
munteanu_2014, Schaerli2014}. For example, the neural subtypes specification
system in the vertebrate neural tube is a two-input network in which
Sonic Hedgehog acts as a morphogen and Olig2 and Nkx2.2 act as the receiver
nodes~\cite{dessaud_dynamic_2010, balaskas2012, exelby_2021}.

@@

% For figure citations, please use "Fig" instead of "Figure".
In order to study three-node GRNs we represented them by three sets of real
numbers, the first set was composed of the interaction values
between genes in the network; the second of the diffusion rates (D) of each of
the three gene products; and the third of the degradation rates ($\delta$) of
these same gene products, with $D \in [0, 0.1]$ and $\delta \in [0, 0.05]$.\\
